\chapter{Suggestions to Improve The Existing System} \label{suggestions}

\section{System Perspective}

\textbf{Context diagram and explanations} of context diagram go here for suggestions to improve the existing system. Plus, other content as appropriate.

Refer to \textit{(Clause 9.6.4, 9.5.4.1)}.


\section{External Interfaces}

\textbf{External Interfaces Class Diagram and its explanations} go here for suggestions to improve the existing system. Plus, other content as appropriate

Refer to \textit{(Clause 9.6.11, 9.5.8)}.

\section{Functions}

\textbf{Use-case diagram} for suggestions to improve the existing system goes here; \textbf{detailed use-case descriptions in a reasonable template} follow. You are expected to have \textbf{about 4 use cases covering suggestions to improve the existing system}. Have some associations in your use-case diagram, e.g. include, extend, specialization. Choose three most complicated use cases. Construct three diagrams \textbf{(one sequence diagram, one activity diagram, and one state diagram)} to elaborate on these three use cases. Plus, other content as appropriate.

Refer to \textit{(Clause 9.6.12, 9.5.5, 9.5.10)}.

\section{Logical Database Requirements}

Key data objects (persistent or not) and their major attributes for suggestions to improve the existing system. Draw the \textbf{Class Diagram} with associations. A class dictionary can be omitted, provided that the naming is understandable.

Refer to \textit{(Clause 9.6.15)}.

\section{Design Constraints}

Specify constraints on the system design imposed by external factors, such as official standards, regulatory requirements, or organizational/managerial limitations for suggestions to improve the existing system.

Refer to \textit{(Clause 9.6.16)}.

\section{System Quality Attributes}
\begin{itemize}
	\item \textbf{Requirement 18 Suggestion:} Automated backup mechanisms shall be implemented to prevent data loss in the event of system failure.
	\item \textbf {Requirement 19 Suggestion:} The system shall be capable of recovering from faults or errors without manual intervention.
	\item \textbf{Requirement 37: Suggestion} The FarmBot software shall be platform-independent and compatible with major operating systems, including Windows, macOS distributions.
	\item \textbf{Reqirement 41: Suggestion?} Sensors and actuators shall provide feedback to users through visual indicators or audible signals to indicate their status or operation. 
	\item \textbf {Requirement 46: Suggestion:} Sensors shall be calibrated regularly to maintain accuracy and reliability over time, with calibration intervals not exceeding [specify duration].
	\item \textbf{Requirement 47: Suggestion} FarmBot Express hardware shall be equipped with a locking and alarm mechanism to prevent theft of its components.  Theft prevention is essential as it resides outside.
\end{itemize}

Important quality attributes (Usability \textit{(Clause 9.6.13, 9.5.6)}, Performance \textit{(Clause 9.6.14, 9.5.7)}, Dependability properties, Maintainability, and so on) in the order of priority with associated requirements for the improved system.

Refer to \textit{(Clause 9.6.18)}.

\section{Supporting Information}

Refer to \textit{(Clause 9.6.20)}.